% 参考文献，此处以 MLA 引用格式为例
\clearpage   %另起一页继续写。这时,你最好使用“\clearpage” 
\begin{thebibliography}{99}
    \bibitem{1} GLOBAL FOREST WHATCH OF AUSTRALIA \\https://www.globalforestwatch.org/topics/fires/?topic=fires\#footer
	\bibitem{2} HU Teng, LIU Zhanjun, LIU Yang, et al. 3D reconnaissance path planning of multiple UAVs. Journal of Systems Engineering and Electronics, 2019, 41(7): 1551-1559.
	\bibitem{3} BASBOUS B. 2D UAV path planning with radar threatening areas using simulated an-nealing algorithm for event detection. The 2018 International Conference on Artificial Intelligence and Data Processing. Malatya, Turkey: IEEE,2018: 1-7.
	\bibitem{4} WANG W F, WU Y C, ZHANG X. Research of the unit decomposing traversal method based on grid method of the mobile robot. Techniques of Automation and Applications, 2013, 32(11): 34-38.
	\bibitem{5} XU Jian, ZHOU Deyun, HUANG He. Multi UAV path planning based on improved ge-netic algorithm. Aeronautical Computing Technique, 2009, 39(4): 43-46.
\end{thebibliography}
\textbf{}The following codes are written by $Python$, which is to collect the data.
\appendix

%\tcblistof[\section]{mcode}{List of MATLAB code}
\section{First Section}
\begin{matlab}{My 1st Code(Written by MATLAB)}{code:labels}
% a comment
clear all, clc
% a comment
x = [1.00; 1.00; 1.00];
beta0 = [1 1 1];
modelfun = 'y ~ k*x^2+b'
mdl = fitnlm(tb,modelfun,beta0)
% a comment
plotResiduals(md1,'fitt111111111111111ed')
%this is a loooooooooooooo ooooooooooooooooooooooooooo oooooooooooooooooog




%1
\end{matlab}
\begin{matlab}{My 2st Code}{code:llabel}
disp('hello')
\end{matlab}
\begin{matlab}{My 2st Code}{code:labell}
    disp('hello')
\end{matlab}
\section{ccODE}
